Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Shorten BCD, resolve a TBD

GHCi's type defaulting~\footnote{%
http://www.haskell.org/ghc/docs/7.4.1/html/users\_guide/interactive-evaluation.html} applies to properties.  If a default type is
not suitable, explicit type-signatures can be used:

@@

\subsection{Applying BDD to Haskell: An Example}
\label{sec:bcp-example}
This section shows how behavior driven development works in practice,
by means of the Fibonacci function.  This is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.

@@

\noindent This first step might appear excessively trivial, but as of now we
already have made some choices with regard to the API of our library.
By giving a usage example, we were forced to think about which
arguments our function takes.  We can now run Doctest to verify that
the example works.

@@

\begin{quote}
\small
\begin{verbatim}
it "returns 0 on negative input" $ do
  fib (-10) `shouldBe` 0
\end{verbatim}
\end{quote}

@@

\noindent It should be the case that fib returns 0 for all negative
numbers, so we state that in the specification:

\noindent Again, our implementation already fulfils that spec.

This concludes our example.  We have seen how to utilize
behavior driven development to incrementally build a small library.
We always extend or adapt the specification first, watch it fail,  and
then tighten the implementation.  The combinators {\tt shouldBe}, {\tt
shouldReturn} and {\tt shouldThrow} can be used to specify behavior of
functions in an intuitive, easy to read manner.

>>>>

GHCi's type defaulting\footnote{%
\url{http://www.haskell.org/ghc/docs/7.4.1/html/users_guide/interactive-evaluation.html#extended-default-rules}
} applies to properties.  If a default type is
not suitable, explicit type-signatures can be used:

@@

\subsection{Applying BDD to Haskell: An Example}
\label{sec:bcp-example}
This section shows how behavior driven development works in practice,
by means of the Fibonacci function.  This is a very simple
example, but the method is also applicable to more complicated
situations where design decisions might not be as obvious as here.

@@

\noindent This first step might appear excessively trivial, but as of now we
already have made some choices with regard to the API of the library.
By giving a usage example, we were forced to think about which
arguments the function takes.  We can now run Doctest to verify that
the example works.

@@

@@

\noindent This concludes our example.  We have seen how to utilize
behavior driven development to incrementally build a small library.
We always extend or adapt the specification first, watch it fail,  and
then tighten the implementation.  The combinators {\tt shouldBe}, {\tt
shouldReturn} and {\tt shouldThrow} can be used to specify behavior of
functions in an intuitive, easy to read manner.
